When does atmospheric dryness drive or reduce evapotranspiration?

### 2017-10-26 doc/eee_symposium/vpd.tex
serious progress, woudl say almost done with slides:

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\graphicspath{{figures/}}

@@

\begin{frame}{Use physically reasonable assumptions to develop a theory.}
Apply a constant uWUE assumption (conserved within plant type; see \cite{Zhou_2016}):
\[uWUE = \frac{GPP \cdot \sqrt{D}}{ET},\]
To derive a new form of Penman-Monteith without implicit ET depedence:
  \[  ET = \frac{\Delta R + \frac{g_a\; P}{T} \left( \frac{ c_p D_{s}}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}}  \frac{\gamma c_s \sqrt{D} }{ R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D}})} \right)\footnote{note that all terms are known }}{ \Delta + \gamma}\]
\end{frame}

\begin{frame}{Recent result (\cite{Zhou_2016}) allows }
  \cite{Zhou_2016} shows that uWUE:
  \[uWUE = \frac{GPP \cdot \sqrt{D}}{ET}\]
  is conserved across space and time (within a plant type).\\
  \medskip
  So we can use uWUE to remove dependence of $g_s$ on $A$:
  \[g_s =  \frac{R \, T}{P} 1.6 \left(1 + \frac{g_1}{\sqrt{D_{s}}}\right) \frac{uWUE \; ET}{c_s \; \sqrt{D}}\]
\end{frame}

\begin{frame}{Derive new form of PM}
  If we plug in our new expression for $g_s$ we can solve for ET to get a new form of PM:
  \[  ET = \frac{\Delta R + \frac{g_a\; P}{T} \left( \frac{ c_p D_{s}}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}}  \frac{\gamma c_s \sqrt{D} }{ R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D}})} \right)\footnote{note that all terms are known, except for $\frac{\text{LAI$_{ref}$}}{\text{LAI}}$} }{ \Delta + \gamma}\]
  Now, we can take derivatives, and:
  \[\frac{\partial \;  ET}{\partial \; D} = \frac{g_a \; P}{T(\Delta + \gamma)}   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
\end{frame}

\section{Results - theory}
\begin{frame}{Scaling Term}
  \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
\begin{figure}
  \includegraphics[width=3.5in]{scaling.png}
  % \caption{}
\end{figure}
\end{frame}

>>>>

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}
\graphicspath{{figures/}}
\DeclareMathOperator{\sign}{sign}

@@

\begin{frame}{Use physically reasonable assumptions to develop a theory.}
Apply a constant uWUE assumption (conserved within plant type; see \cite{Zhou_2016}):
\[uWUE = \frac{GPP \cdot \sqrt{D}}{ET},\]
To derive a new form of Penman-Monteith without implicit ET depedence:
  \[  ET = \frac{\Delta R + \frac{g_a\; P}{T} \left( \frac{ c_p D_{s}}{R_{air}} -  \frac{\gamma c_s \sqrt{D} }{ R* \; 1.6 \text{ uWUE } (1 + \frac{g_1}{\sqrt{D}})} \right)\footnote{note that all terms are known }}{ \Delta + \gamma}\]
\end{frame}

\begin{frame}{Use physically reasonable assumptions to develop a theory.}
  With our new form of Penman-Monteith we can now take derivatives, giving:
  \[\frac{\partial \;  ET}{\partial \; D} = \frac{2 g_a \; P}{T(\Delta + \gamma)}   \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
  In the interest of time, we will just focus in the ``sign'' term:
  \[\sign \left[\frac{\partial \;  ET}{\partial \; D}\right] = \sign \left[  \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right) \right] \]

\end{frame}

\section{Results - theory}
\begin{frame}{Consequences of theory - ``sign'' term}
  \[ \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
  \begin{itemize}
  \item $c_p$ and $R*$ are constants
  \item $R_{air}$, $c_s$, and $\gamma$ are approximately constant (relative to $\sqrt{D}$)
  \item uWUE and g_1 are constants within plant type (i.e. grass, grops, deciduous forest, evergreen needleleaf forest, shrub)
  \item Which leaves D = VPD
  \end{itemize}
  So within each plant type, whether the atmospheric demand (ET increasing with VPD) or plant response (ET decreasing with VPD) dominates is essentially just a function of VPD!
\end{frame}

\begin{frame}{Consequences of theory - ``sign'' term}
  shoe expression for when d et dvpd < 0
  \begin{itemize}
  \item $c_p$ and $R*$ are constants
  \item $R_{air}$, $c_s$, and $\gamma$ are approximately constant (relative to $\sqrt{D}$)
  \item uWUE and g_1 are constants within plant type (i.e. grass, grops, deciduous forest, evergreen needleleaf forest, shrub)
  \item Which leaves D = VPD
  \end{itemize}
  So within each plant type, whether the atmospheric demand (ET increasing with VPD) or plant response (ET decreasing with VPD) dominates is essentially just a function of VPD!
\end{frame}
